Old or Heavy?\\Decaying Gracefully with Age/Weight Shapes.

### 2019-05-24 papers/CADE19/paper.tex
update table 5

\begin{table}[t]
	\caption{
Total number of problems solved compared to other solvers.
}
	\centering
	\begin{tabular}{l l l}
	Solver~~ & Total solved~~~ & Uniquely solved \\
	\hline
	Vampire (old)	& 13,057 & 0\\
	Vampire (new)   & 13,191 & 54\\
	E 		& 10,845 & 190\\
	iProver		& 8,143 & 215\\
	CVC4		& 9,354 & 501\\
	\end{tabular}
	\label{tab:other}
\end{table}

>>>>

\begin{table}[t]
	\caption{
Total number of problems solved compared to other solvers.
}
	\centering
	\begin{tabular}{l l l l}
	Solver~~ & Total solved~~~ & \multicolumn{2}{c}{Uniquely solved}  \\
	& & All ~~~~~& Excluding Vampire (old) \\
	\hline
	Vampire (old)	& 13,057 & 0 & -\\
	Vampire (new)   & 13,191 & 54 & 1030\\
	E 		& 10,845 & 190 & 190\\
	iProver		& 8,143 & 215 & 215\\
	CVC4		& 9,354 & 501 & 502\\
	\end{tabular}
	\label{tab:other}
\end{table}
